Analyzing the impact of social attributes on the success of commit integration

### 2017-02-18 Paper/MSRChallenge2017.tex
minor revisions

To collect the social data, we created a web crawler to extract the social data
from developer's profiles.
We used the commit hash and the project name in the original data
set~\cite{msr17challenge} to locate the webpage of the commit using the syntax
below. 
\newline \newline
\textit{https://github.com/\textbf{NameOfProject}/commit/\textbf{CommitHash}}
\newline \newline
Then, we scraped the commit author's
\textit{username} from the page. If the scrapper was able to find username, the
scraper went to the user's profile information using the syntax below.
\newline \newline
\textit{https://github.com/\textbf{UserName}}
\newline \newline
The scrapper then extracted the following items from the user's profile.
\begin{itemize}
\item Repositories
\item Stars
\item Followers
\item Following
\item Contributions 
\end{itemize}

>>>>

To collect the social data, we created a web scrapper to extract the social data
from developer's profiles.
We used the commit hash and the project name in the original data
set~\cite{msr17challenge} to locate the web page of the commit using the syntax
below. 
\newline \newline
\textit{https://github.com/\textbf{NameOfProject}/commit/\textbf{CommitHash}}
\newline \newline
Then, we scraped the commit author's
\textit{username} from the page. If the scrapper was able to find username, the
scraper went to the user's profile information using the syntax below.
\newline \newline
\textit{https://github.com/\textbf{UserName}}
\newline \newline
The scrapper then extracted the following items from the user's profile.
\begin{itemize}
\item Repositories
\item Stars
\item Followers
\item Following
\item Contributions 
\end{itemize}
